% Awesome resume LaTeX Template for Resume
%
% This template has been downloaded from:
% https://github.com/abdelazeem201/resume
%
% Author:
% Ahmed Abdelazeem <a.abdelazeem201@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[9]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{#1}{\color{black}{\LARGE {\underline{#2}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#3}{\underline{#3}} $\mid$
      #4 $\mid$
      #5 : \href{#6}{\underline{#7}} $\mid$
      #8 : \href{#9}{\underline{#7}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1 in \textbf{#2}}  & {#3}\\
    {\textit{#4}} & {#5}\\\vspace{-18pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}

\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\coureseItem}[2]{
	\vspace{-1pt}
	\item
	\begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
		{\textbf{#1}. } & {#2}
	\end{tabular*}\vspace{-17pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}

\begin{document}

%   HERO   %
\head
  {https://abdelazeem201.github.io/}
  {Ahmed Abdelazeem}
  {a.abdelazeem201@gmail.com}
  {+20 102-876-8232}
  {Github}
  {https://github.com/abdelazeem201}
  {Abdelazeem}
  {LinkedIn}
  {https://www.linkedin.com/in/ahmed-abdelazeem/}

%   SUMMARY   %
\section{Summary}
\sectionStart
  \summaryText
  {Well-versed in physical design implementation of chips and digital processors. Looking for an opportunity to
  	work as a physical design engineer where I can utilize my skills to enhance my knowledge in Circuit Design, SoC
  	and ASIC Back-end flow.}
\sectionEnd

%   EDUCATION   %
\section{Education}
\sectionStart
  \educationItem
    {Bachelor of Engineering in } 
    {Electronics and communications} 
    {July 2016 - June 2021}
    {Zagazig University} 
    {\textbf{Very Good}}
    {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Relevant Coursework:} Electric Circuits, Electronic Devices and Circuits, Logic Design, Signal and Systems, Digital Signal Processing, CMOS Integrated Circuits, Computer Organization and Architecture, VLSI Modeling and Design}}}
\sectionEnd

%   SKILLS   %
\section{Technical Skills}
\sectionStart
\skillItem
{Languages}
{C, Python, Matlab}
\skillItem
{HDL}
{Verilog, VHDL}
   \skillItem
{Logic Synthesis}
{DC(Synopsys), Genus(Cadence)}
 \skillItem
{Place \& Route}
{ICC(Synopsys), Innovus(Cadence)}  
    \skillItem
{Physical Verification}
{LVS, DRC, ERC, Density rules}
\skillItem
{Other Tools}
{Vivado, VCS, QuestaSim, PrimeTime, Calibre, Cadence Virtuoso, HSpice}
\skillItem
{Technologies/Frameworks}
{Linux, GitHub, Git, \LaTeX\ }
\vspace{3pt}
\sectionEnd

%   EXPERIENCE   %
\section{Experience}
\sectionStart
\jobHeading
{FPGA Design Engineer}
{Dec 2021 - Dec 2022}
{Military Conscription, Benha Electronics Co.}
\listStart
\bulletItem
{Designed and implemented FPGA-based solutions for the military services, including signal processing systems for the
	Air Defense Forces Research and Development department as part of my obligatory military service.}
\listEnd
\jobHeading
{ASIC Physical Design Intern}
{Jul 2022 - Sep 2022}
{ICpedia}
\listStart
\bulletItem
{Responsible for Physical Implementation of an IP: starting from Netlist to GDS, including floorplanning, Placement, Clock design, Optimization, Timing closure, DRC/LVS, and sign-off.}
\listEnd
\jobHeading
{ASIC Physical Design Intern}
{Apr 2021 - Apr 2021}
{Synopsys}
\listStart
\bulletItem
{Responsible for the entire PNR flow for the ORCA TOP chip using DC and IC Compiler using ”SAED 32/28nm PDK” with 50K
	- 60K gates and operates at 60MHz frequency. and also have worked on PT for learning the basics of STA.}
\listEnd
\jobHeading
{ASIC Physical Design Intern}
{Jan 2021 - Feb 2021}
{Cadence}
\listStart
\bulletItem
{ 7-Days hands-on workshop: to learn and run complete synthesis and Implementation flow on a design with the given
	specifications and optimize it for PPA with Cadence Genus Synthesis and Innovus.}
\listEnd
\jobHeading
{ASIC Design Intern}
{Dec 2020 - Dec 2020}
{Arm Ltd}
\listStart
\bulletItem
{ 5-Day hands-on workshop: to develop Arm Cortex-M0 based SoCs, from creating high-level functional specifications to
	design, implementation, and testing on FPGA platforms using standard HDL and software programming languages.}
\listEnd

\jobHeading
{ASIC Physical Design Intern}
{Aug 2020 - Nov 2020}
{One Lab.}
\listStart
\bulletItem
{RTL to GDSII: going through digital design flow starting from Constraint, Synthesis, PnR steps, Timing, Sign off, and
	Physical verification. Making sure to meet PPA and physical specifications until the design is clean to be fabricated}
\listEnd
\sectionEnd

%   PROJECTS   %
\section{Projects}
\sectionStart
  \projectHeading
    {}
    {\textbf{High-Speed Microcontroller for Display intensive Application, GP}}
    {}
    {Sep 2020 - July 2021}
  \listStart
    \bulletItem
      {I was responsible for the complete physical design of 180nm Digital Top block and also to IP harden the CORTEX-M0
      	sub chip. Did the entire PnR flow using Cadence Encounter for the same and also the STA using PrimeTime and
      	physical verification for both the hardened IP and Digital Top block.}
  \listEnd
  \projectHeading
  {https://github.com/abdelazeem201/Mini-Stereo-Digital-Audio-Processor-MSDAP}
  {MSDAP Chip Design}
  {(Verilog, C, FPGA)}
  {Jan 2021 - Mar2021}
  \listStart
  \bulletItem
  {Developed Verilog RTL code for high speed, low power MSDAP- ASIC chip using Xilinx ISE consisting of a Controller,
  	ALU, Memories and serial communication unit, and verified the system functionality in C. aslo I synthesized the design
  	in Design Compiler \& Performed pre-layout simulation in Modelsim. And also developed Final Physical Design using
  	the IC Compiler, Performed Clock Tree Synthesis, Optimization, Parasitic (RC) extraction, Static Timing Analysis
  	(STA).}
  \listEnd
  \projectHeading
    {https://github.com/abdelazeem201/ASIC-Implementation-UART}
    {Design and Implementation of UART}
    {(Verilog, System-Verilog, FPGA)}
    {Sep 2020 - Nov 2020}
  \listStart
    \bulletItem
      { Complete the Digital Design Flow from the RTL2GDS using 45nm Free PDK. synthesized the verilog code using DC
      	Compiler, and aslo did the entire PnR flow using Synopsys IC Compiler.}
  \listEnd
  \projectHeading
    {https://github.com/abdelazeem201/5-Stage-Pipeline-RISC-V-RV32I}
    {Design and Implementation of 32 – bit RISC Processor}
    {(Verilog, VHDL, FPGA)}
    {Oct 2019 - May 2020}
  \listStart
    \bulletItem
      {Implemented the behavioral model of a 32-bit microprocessor using VHDL on Altera Cyclone IV FPGA}
  \bulletItem
      {Complete the Digital Design Flow of the RISC using 45nm, with 10 metal layers, and 500MHZ frequency. Synthesized
      	the VHDL code in DC Compiler}
        \bulletItem
      {Developed Final Physical Design using the IC Compiler. Performed Clock Tree Synthesis, Optimization, Parasitic (RC)
      	extraction using PrimeTime., Static Timing Analysis (STA).}
  \listEnd
\sectionEnd

%   COURSES   %
\section{COURSES}
  \sectionStart
	\coureseItem
	{C Programming}
	{Udemy,2017}
\coureseItem
{Hardware Modeling using Verilog by Prof. Indranil Sengupta}
{YouTube,2018}
\coureseItem
{Introduction to FPGA Design for Embedded Systems}
{Coursera,2018}
\coureseItem
{CMOS Analog IC Design by Prof. Hesham Omran}
{Mahara-Tech ,2019}
\coureseItem
{VLSI CAD Part II: Layout by Rob A. Rutenbar}
{Coursera,2019}	
\coureseItem
{Python and Data Structures}
{Coursera,2020}
\coureseItem
{Digital VLSI Design (RTL2GDS) by Prof. Adam Teman}
{YouTube,2020}
\coureseItem
{VLSI Physical Design by Prof. Indranil Sengupta}
{YouTube,2020}		
\coureseItem
{VSD - Static Timing Analysis - I \& II}
{Udemy,2022}
\coureseItem
{VSD - Physical Design Flow}
{Udemy,2022}
\coureseItem
{UPF Power Aware Design \& Verification by Robin Garg}
{Udemy,2022}
\sectionEnd
%   EXTRA-CIRRUCULAR   %
\section{EXTRA-CIRRUCULAR}
\sectionStart
  \jobHeading
    {Project Management}
    {Jan 2019 - Feb 2020}
    {Enactus ZU}
  \listStart
  \bulletItem
  	{Conducting several types of research and analysis on the 17 SDGs and connecting them to local problems.}
    \bulletItem
    {Prepare clear and concise reports, proposals, and other written materials of a technical nature}
    \bulletItem
    {Design, implement, and manage ongoing projects and direct the related resources and activities to successful completion.}
  \listEnd
  \jobHeading
    {PR director}
    {Jan 2018 - Sep 2018}
    {Hult Prize Foundation, ZU}
  \listStart
    \bulletItem
    {Negotiating and receiving governmental and non-governmental grants up to 40,000 EGP}
  \listEnd
\sectionEnd

\end{document}